---
title: "Micro-Claims Analysis and Modelling: Claim Status and Payment Model"
author: "Jimmy Briggs"
date: "May 9, 2016"
output:
  html_notebook: 
    toc: yes
    toc_depth: 2
    code_folding: hide
    highlight: tango
    theme: readable
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 2
    code_folding: hide
    theme: readable
    highlight: tango
    number_sections: yes
resource_files:
- index_files/figure-html/zm_plots-1.png
- index_files/figure-html/unnamed-chunk-4-1.png
- index_files/figure-html/sim_v_actual-1.png
- index_files/figure-html/cm_logit_plot-1.png
runtime: shiny
---

```{r setup, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE, error = FALSE,
  cache = TRUE, autodep = TRUE
)
```

[Source Code](https://github.com/jimbrig/claims-pm)

# Introduction

## Purpose and Scope

This report describes a model for predicting incremental paid losses on
an individual claim basis ("The Model"). The model uses a mixture of
predictive modeling and simulation techniques to mimic real world claim
development.

Note that this report is a much more simplified version of the full
ensemble of model's used in the full analysis performed and is merely
meant as a starting point for teaching/learning purposes.

## Background

Models, by definition, use simplified assumptions of reality to reveal
information or predict events based on the underlying data. Models which
closely mimic the fundamental forces driving the data have the best
chance of providing valuable insights.

Due to data and computing limitations, actuaries have traditionally
aggregated loss information by policy, accident, or calendar period to
project future losses. By aggregating losses, the actuary loses valuable
claim level information.

The model assumes that individual claims and their claim level
characteristics are the fundamental drivers of future payments.
Therefore, In accordance with the philosophy that the best models are
those which mimic reality most closely, the model uses information on an
individual claim level, and runs statistically rigorous techniques to
fit and simulate individual claim development.

## Overview

The model is meant to be a starting point for anyone looking to discover
new and advanced methods for performing micro-claims analysis and
machine-learning modelling techniques that provide insights beyond the
typical aggregated actuarial practices in P&C. Additionally, the model
is a showcase for the statistical power that the R Programming language
can provide, specifically for those with apriori statistical and
mathematical knowledge in applied predictive analytics and probability
theory.

I decided to use only a few very common predictor variables so the model
could easily be applied to other data sets. For transparency and to aid
interested individuals, I provide this report with access to the `R`
code used to fit and run predictions. The code can be viewed by clicking
the `code` boxes on the right side of the report. The `R` savvy reader
can run the `R` code to reproduce the output, apply the model to other
data sets, and expand and improve upon the model.

The model is only applicable to reported claims and their corresponding
incremental payments. IBNR claim predictions are beyond the scope of
this model.

## Vocabulary

For consistency and clarity I use the following terms:

-   **Response Variable** The value being predicted by the model (claim
    status and claim incremental payment in this report)
-   **Predictor Variable** The values used to fit the model or to
    predict the response variable (i.e. I use certain claim
    characteristics as predictor variable to model and predict the
    response variable)

## Data

In the spirit of mimicking the real world, this report communicates the
model through a working example using real auto-liability data supplied
mostly from the [insuranceData R
Package](https://cran.r-project.org/web/packages/insuranceData/insuranceData.pdf)
([GitHub Repo](https://github.com/cran/insuranceData)) as well as
publicly available data supplied by the **CAS**.

Note that this specific model has been tuned to form predictions related
specifically to *Bodily Injury* claims only, as these claims drive the
foundation of the risk behind Auto Liability reserving and rate-making.

That being said, although the results of the model are specific to Auto
Liability in this instance, the modeling techniques and machine-learned
tuning procedures can easily be generalized to other lines of coverage,
areas of business, and risk portfolios.

-   R Code for Data Load and Ingestion:

```{r load_data, message=FALSE}
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(caret, warn.conflicts = FALSE)
library(lubridate)
library(ggplot2, warn.conflicts = FALSE)
library(knitr)
library(DiagrammeR)
library(scales)
library(shiny)
require(e1071) 
require(bindrcpp)
library(qs)
library(webshot)

# turn off scientific notation in printing
options(scipen = 999)

# load data
claims <- qs::qread("model-claims.qs")

# development age to project from
# e.g. if I set this to 18 I will use information available
# as of the 18 month evaluation to predict stuff at age 30)
devt_period <- 30

# year to predict with model
# evaluations at or greater than this time will not be included in
# the model fit
predict_eval <- as.Date("2010-11-30")

# remove unneeded data
claims <- dplyr::filter(claims, 
                        eval <= predict_eval,
                        eval >= predict_eval - years(5)) %>%
            dplyr::select(eval, devt, claim_number, 
                          status, tot_rx, tot_pd_incr,
                          status_act, tot_pd_incr_act)

devt_periods_needed <- seq(6, devt_period + 12, by = 12)

# for showing in triangle
claims_display <- dplyr::filter(claims, devt %in% devt_periods_needed)

# only need the claims at the selected `dev_period`
claims <- dplyr::filter(claims, devt %in% devt_period)
```

I am using data from fiscal years 2003 to
`r lubridate::year(predict_eval) + 1`.

Fiscal years begin at 6/1 of the year prior to the fiscal year and end
at 5/31 of the fiscal year (i.e. fiscal year 2003 includes claims which
occurred between 6/1/2002 and 5/31/2003).

The claims are evaluated at 11/30 of each year from 2002 to
`r lubridate::year(predict_eval)`.

I created a large data set containing all the data used in fitting the
model and making predictions from the model.

The original data and the script used to prepare the large data set used
in this report is located in the `data/` directory and details can be
viewed in this report's Appendix.

# The Model

The model uses several advanced statistical techniques. For compactness
and because I lack the expertise to explain everything in detail, a
comprehensive explanation of these techniques is beyond the scope of
this analysis.

Where-ever possible I have included links to additional resources for
diving into the statistics behind the model. The statistics will be only
very briefly touched upon as each technique is used in the model fit.

### Train and Test Data

The first step in fitting the model is to feed training data into the
model.

I am using all data from fiscal years prior to
`r lubridate::year(predict_eval) + 1` from development time
`r devt_period` months to `r devt_period + 12` months to fit the model.

Later I will pass the test data (i.e. claims from fiscal year
`r lubridate::year(predict_eval) + 1` at `r devt_period` months) to
predict the status of each of these claims at `r devt_period + 12`
months and the incremental payment per claim from `r devt_period` to
`r devt_period + 12` months.

## Model Overview Diagram

The following diagram illustrates how the model is fit:

```{r diagram1}
mermaid("
  graph TD
  A(Claim Train Data)-->B{Fit Closure Model}
  A(Claim Train Data)-->C[Remove Closed-Closed]
  A(Claim Train Data)-->D[Remove Zero Paid]
  C-->E{Fit Zero Model}
  D-->F{Fit Payment Model}
")
```

After fitting the models (pictured as a rhombus in the above diagram)
with the claims training data I can use the three models to predict a
probability for status and zero payment or a dollar value for
incremental payments on the test data.

The claims test data flows through the following diagram to arrive at
the final output:

```{r diagram2, echo=FALSE}
mermaid("
  graph TD
  A(Claim Test Data)-->B{Closure Model + Simulation}
  B-->C(Claims Simulated to be Closed Closed)
  B-->D(All Other Claims)
  D-->E{Zero Model + Simulation}
  E-->F(Claims Simulated with Zero Payment)
  E-->G(Claims Simulated with Payment)
  G-->H{Payment Model + Simulation}
  H-->J(Output: Claims with Simulated Status and Payment)
  C-->I[Simulated Payment set to Zero]
  F-->I[Simulated Payment set to Zero]
  I-->J
", height = 700)
```

At each model (pictured as a rhombus in the above diagram) the claim in
the test data is given a predicted value based on the model. I then run
a simulation based on this predicted value to model real world
variability.

At each step the simulated claims are passed to the next model based on
the results of the simulation in the previous model's simulated
results/probabilities.

## Claim Closure Model

### Assumptions

To predict whether a claim will close within a given period of time, I
use a logistic regression with *center, scale, and
[Yeo-Johnson](https://www.stat.umn.edu/arc/yjpower.pdf) transformations*
applied to all continuous predictor variables.

I am modeling the following variables:

**Response Variable**

-   *status_act* Actual claim status at `r devt_period + 12` months.

**Predictor Variables**

-   *status* Claim status at `r devt_period` months ("C" for Closed and
    "O" for open).
-   *tot_rx* Total case reserve dollar value at `r devt_period`.
-   *tot_pd_incr* Total incremental paid loss dollar value between
    `r devt_period - 12` months and `r devt_period` months.

### Data Preparation

```{r cm_data_prep}
# remove data the same valuation or newer than the prediction eval
# Only claims from valuations before the valuation I am predicting will be used
# to fit the model
model_data <- dplyr::filter(claims, eval < predict_eval)
```

### Model Fit

The model fit uses **10-fold cross validation** to optimize coefficient
estimation and a *stepwise Akaiki Information Critereon (AIC)* algorithm
for feature selection:

```{r cm_model_fit, message=FALSE, warning=FALSE}
cm_model <- caret::train(status_act ~ status + tot_rx + tot_pd_incr, 
                         data = model_data,
                         method = "glmStepAIC",
                         trace = FALSE,
                         preProcess = c("center", "scale", "YeoJohnson"),
                         trControl = trainControl(method = "repeatedcv", 
                                                  repeats = 2))
```

```{r cm_summary, results = "asis"}
cm_summary <- cm_model$results[, -1]

kable(cm_summary,
      digits = 5,
      row.names = FALSE)
```

For a more detailed statistical summary of the claim closure model fits
see Appendix `cm_summary`

```{r cm_prob, warning=FALSE, message=FALSE}
cm_probs <- cbind(model_data, predict(cm_model, 
                                      newdata = model_data, 
                                      type = "prob"))
# find the logit value
cm_probs$logits <- log(cm_probs$O / cm_probs$C)
```

In the plots below the blue line indicates the fitted probability of the
claim at age `r devt_period` months being open at age
`r devt_period + 12` months.

The red dots at the top and bottom are the actual status for the
training data at `r devt_period + 12` months (i.e. model fits the blue
line to the red dots).

```{r cm_logit_plot, fig.height=3, warning=FALSE}
cm_probs$status_act <- ifelse(cm_probs$status_act == "C", 0, 1)
  
ggplot(cm_probs, aes(x = logits, y = status_act)) +
       geom_point(colour = "red", 
                  position = position_jitter(height = 0.1, width = 0.1),
                  size = 0.5,
                  alpha = 0.2) + 
       geom_smooth(method = "glm", method.args = list(family = "binomial"), 
                   size = 1) + 
       ylab("Probability Open") +
       xlab("Logit Odds") +
       ggtitle(paste0("Age ", devt_period, " to ", devt_period + 12, " Months Claim Open Probabilities"))
```

## Zero Payment Model

### Assumptions

The zero payment model is similar to the claim closure model in that I
am looking at a *binomial response variable*. I am modeling whether the
claim has zero or nonzero incremental payments.

I remove all claims that have a status at `r devt_period` months of
closed and a status of closed at `r devt_period + 12` (I refer to these
claims as `closed-closed` claims). 

Additionally, I assume that all of these claims will ultimately have zero incremental payments in the final payment model.

**Reponse Variable**

-   *zero* Factor indicating whether the claim had zero or nonzero
    incremental payments between age `r devt_period` months and
    `r devt_period + 12` months.

**Predictor Variables**

-   *status_act* Actual claim status at `r devt_period + 12` months
    ("C"" for Closed and "O"" for open).
-   *status* Claim status at `r devt_period` months
-   *tot_rx* Total case reserve dollar value at `r devt_period` months.
-   *tot_pd_incr* Total incremental paid loss dollar value between
    `r devt_period - 12` months and `r devt_period` months.

Note: I could use `status_act` as a predictor variable here because for
the test data I will simulate the status at `r devt_period + 12` first
and then use that simulated status as a predictor variable in the zero
payment model.

### Data Prep

```{r zm_data_prep}
# remove all claims that have a closed closed status from the data
# these will be set to incremental payments of 0
zm_model_data <- filter(model_data, status == "O" |  status_act == "O")

# Add in response variable for zero payment:
zm_model_data$zero <- factor(ifelse(zm_model_data$tot_pd_incr_act == 0, 
                                    "Zero", "NonZero"))
```

### Fit

I use the same data prepared for the claim closure model to fit the zero
payment model.

```{r zm_model_fit, cache=TRUE, message = FALSE, warning = FALSE}
zm_model <- caret::train(zero ~ status + status_act + tot_rx + tot_pd_incr, 
                         data = zm_model_data,
                         method = "glmStepAIC",
                         trace = FALSE,
                         preProcess = c("center", "scale", "YeoJohnson"),
                         trControl = trainControl(method = "repeatedcv", 
                                                  repeats = 2))
```

```{r zm_summary, results = "asis"}
zm_summary <- zm_model$results[, -1]

kable(zm_summary,
      row.names = FALSE)
```

```{r zm_prob, warning=FALSE, message=FALSE}
zm_probs <- cbind(zm_model_data, predict(zm_model, 
                                         newdata = zm_model_data, 
                                         type = "prob"))

zm_probs$logits <- log(zm_probs$NonZero / zm_probs$Zero)
```

In the plots below, the blue line indicates the fitted probability of
the claim having a payments between age `r devt_period` and
`r devt_period + 12` months. The red dots at the top are the actual
claims with payments between age `r devt_period` and
`r devt_period + 12` months, and the dots at the bottom are the claims
with zero payments during this time period. (i.e. Zero Payment model
fits the blue line to the red dots)

```{r zm_plots, fig.height=3, warning=FALSE}
zm_probs$zero <- ifelse(zm_probs$zero == "Zero", 0, 1)
  
ggplot(zm_probs, aes(x = logits, y = zero)) +
       geom_point(colour = "red", 
                  position = position_jitter(height = 0.1, width = 0.1),
                  size = 0.5,
                  alpha = 0.2) + 
       geom_smooth(method = "glm", method.args = list(family = "binomial"), 
                   size = 1) + 
       ylab("Payment Probability") +
       xlab("Logit Odds") +
       ggtitle(paste0("Age ", devt_period, " to ", devt_period + 12, 
                      " Non-Zero Incremental Payment"))
```

## Incremental Payment Model

### Assumptions

The incremental payment model models incremental payments between
`r devt_period` and `r devt_period + 12`. The incremental payment model
uses a generalized additive model (GAM) with an integrated smoothness
estimation and a **quasi-poisson log link function** ;).

**Response Variable**

-   *tot_pd_incr_act* Total incremental payment between `r devt_period`
    and `r devt_period + 12` months.

**Predictor Variables**

-   *status_act* The actual status at `r devt_period + 12` months.
-   *tot_rx* Total case reserve dollar value at `r devt_period` months.
-   *tot_pd_incr* Incremental payments between `r devt_period - 12` and
    `r devt_period` months.

### Data Prep

```{r payment_data_prep}
#Take out zero pmnts:
nzm_model_data <- zm_model_data[zm_model_data$tot_pd_incr_act > 0, ]
```

### Fit

```{r nzm_model_fit}
# fit incremental payment model
nzm_model <- mgcv::gam(tot_pd_incr_act ~ status_act + s(tot_rx) + s(tot_pd_incr),
                       data = nzm_model_data,
                       family = quasipoisson(link = "log"))
```

```{r nzm_predict_training, warning=FALSE, message=FALSE}
nzm_fit <- cbind(nzm_model_data, 
                 tot_pd_incr_sim = exp(predict(nzm_model, newdata = nzm_model_data)))
```

```{r nzm_plots, fig.height=3, warning=FALSE}
# plots to be determined
```

# Simulation

## Closure Status

```{r cm_predict, cache = TRUE}
set.seed(1234)
n_sims <- 2000

cm_pred_data <- dplyr::filter(claims, eval == predict_eval)

cm_probs <- cbind(cm_pred_data, 
                  predict(cm_model, newdata = cm_pred_data, type = "prob"))
  
cm_pred <- lapply(cm_probs$O, rbinom, n = n_sims, size = 1)
cm_pred <- matrix(unlist(cm_pred), ncol = n_sims, byrow = TRUE)
cm_pred <- ifelse(cm_pred == 1, "O", "C")
cm_pred <- as.data.frame(cm_pred)
```

I use the probabilities returned from the closure model to simulate the
status of all of the claims.

I simulate each claim `r n_sims` times.

The table below shows selected age `r devt_period` claims after they had
their closure probability predicted by the closure model and their
status simulated using a simulated binomial random variable.

```{r cm_predict_table, results = "asis"}
cm_out <- cm_probs

cm_out <- dplyr::select(cm_out, claim_number, status, tot_rx, tot_pd_incr, O)

cm_out$status_sim <- cm_pred[, 1]
cm_out <- cm_out[c(1, 6, 24, 2, 10), ]
names(cm_out) <- c("Claim Number", "Status", "Case", "Paid Incre", 
                   "Prob Open", "Sim Status")
kable(cm_out,
      row.names = FALSE)
```

The `Prob Open` column is the probability that the age `r devt_period`
claim will be open at age `r devt_period + 12` as modeled in the closure
model. The `Sim Status` column is the result of a *Bernoulli simulation*
on each of those probabilities.

I am running this simulation `r n_sims` times to simulate `r n_sims`
closure scenarios.

The simulations allow me to determine the corresponding distribution's
confidence intervals.

## Zero Payment Model

Next the simulated claims with their simulated statuses have their
probability of having a non zero incremental payment simulated by the
zero payment model. This probability is then simulated using the same
random binomial simulation approach as used when simulating closure
status.

```{r zm_predict_data_prep}
# put closure model predictions together
cm_pred <- cbind(cm_probs[, c("claim_number"), drop = FALSE], cm_pred)

# gather `cm_pred` into a long data frame
cm_pred <- tidyr::gather(cm_pred, key = "sim_num", 
                         value = "status_sim", 
                         -claim_number)

# join `zm_pred_data` to predictions from closure model
# remove status_act and rename the simulated states as status_act
zm_pred_data <- left_join(cm_pred, cm_probs, by = "claim_number") %>%
                  dplyr::select(-status_act) %>%
                  dplyr::rename(status_act = status_sim)

# remove all claims that have a closed closed status from the data
# these will be set to incremental payments of 0 
closed_closed_data <- dplyr::filter(zm_pred_data, status == "C" &  status_act == "C")

zm_pred_data <- filter(zm_pred_data, status == "O" |  status_act == "O")
```

```{r zm_predict, cache = TRUE}
zm_pred <- cbind(zm_pred_data, 
                  predict(zm_model, newdata = zm_pred_data, type = "prob"))
  
zm_pred$zero_sim <- sapply(zm_pred$NonZero, rbinom, n = 1, size = 1)
zm_pred$zero_sim <- ifelse(zm_pred$zero_sim == 1, "NonZero", "Zero")
```

```{r zm_predict_table, results = "asis"}
zm_out <- zm_pred

zm_out <- dplyr::select(zm_out, claim_number, status, tot_rx, tot_pd_incr, 
                        status_act, NonZero, zero_sim)

zm_out <- head(zm_out, 8)
names(zm_out) <- c("Claim Number", "Status", "Case", "Paid Incre", 
                   "Sim Status", "Prob Non Zero", "Zero Sim")
kable(zm_out,
      row.names = FALSE)
```

## Incremental Payment Simulation

Since I am only interested in predicting incremental payments for claims
that were simulated to have a non-zero incremental payment, all claims
that were closed at age `r devt_period` and were simulated to be closed
at `r devt_period + 12` will be given an incremental payment of zero.

Additionally, all claims that were simulated by the Zero Payment Model
to have a Zero payment will be given an incremental payment of zero.

```{r nzm_predict_data_prep}
# separate zeros from non zeros
zero_claims <- filter(zm_pred, zero_sim == "Zero")

nzm_pred <- filter(zm_pred, zero_sim == "NonZero")
```

Now for the final simulations I simulate all the claims that were
predicted to have a non-zero incremental payment.

```{r nzm_predict, cache = TRUE}
### Quasi Poisson Simulation
nzm_pred$tot_pd_incr_fit <- exp(predict(nzm_model, newdata = nzm_pred))

# use negative binomial to randomly disperse claims from predicted fit
nzm_pred$tot_pd_incr_sim <- sapply(nzm_pred$tot_pd_incr_fit,
                                    function(x) {
                                      rnbinom(n = 1, size = x ^ (1/5), prob = 1 / (1 + x ^ (4/5))) 
                                    })
```

```{r combine_predictions}
closed_closed_data$tot_pd_incr_sim <- 0
zero_claims$tot_pd_incr_sim <- 0

closed_closed_data$sim_type <- "Close_Close"
zero_claims$sim_type <- "Zero"
nzm_pred$sim_type <- "Non_Zero"


cols <- c("sim_num", "claim_number", "status_act", "tot_pd_incr_sim", "sim_type")

sim_1 <- closed_closed_data[, cols]
sim_2 <- zero_claims[, cols]
sim_3 <- nzm_pred[, cols]


full_sim <- rbind(sim_1, sim_2, sim_3)

kable(
  full_sim[sample(1:nrow(full_sim), 20), ], 
  row.names = FALSE,
  col.names = c("Sim Num", "Claim Num", "Sim Status", "Sim Payment", "Sim Type"))
```

## Results

### All Claims Aggregated by Simulation

```{r agg}
# find actual number of open claims and incremental payment dollars
pred_data_actuals <- mutate(cm_pred_data, status_act = ifelse(status_act == "C", 0, 1))

open_actual <- sum(pred_data_actuals$status_act)
payments_actual <- sum(pred_data_actuals$tot_pd_incr_act)
```

The blue dashed vertical line marks the actual number of open claims in
the test data at `r devt_period + 12` months development. The white
histogram shows the simulated distribution of open claims at
`r devt_period + 12` as determined from the simulation based on the
claim closure model.

```{r sim_v_actual, fig.height = 3, warning=FALSE, message=FALSE}
full_sim_agg <- mutate(full_sim, open = ifelse(status_act == "C", 0, 1)) %>%
                  group_by(sim_num) %>%
                  summarise(n = n(),
                            open_claims = sum(open),
                            incremental_paid = sum(tot_pd_incr_sim))


ggplot(full_sim_agg, aes(x = open_claims)) +
  geom_histogram(fill = "white", colour = "black") +
  ggtitle("Histogram of Simulated Open Claim Counts") +
  ylab("Number of Observations") +
  xlab("Open Claim Counts") +
  geom_vline(xintercept = open_actual, size = 1, 
             colour = "blue", linetype = "longdash")
```

The blue dashed vertical line marks the actual incremental payments in
the test data between age `r devt_period` and `r devt_period + 12`. The
white histogram shows the simulated distribution of incremental payments
between age `r devt_period` and `r devt_period + 12` months for all
claims in the test data. The simulation is based on the incremental
payment model.

```{r plot}
ggplot(full_sim_agg, aes(x = incremental_paid)) +
  geom_histogram(fill = "white", colour = "black") +
  ggtitle("Histogram of Simulated Incremental Payments") +
  ylab("Number of Observations") +
  xlab("Incremental Payments") +
  geom_vline(xintercept = payments_actual, size = 1, 
             colour = "blue", linetype = "longdash") +
  scale_x_continuous(labels = dollar)
```

### Individual Claim

The blue dashed vertical line marks the actual incremental payments in
the test data for the claim in the `Select Claim Number` input box
between age `r devt_period` and `r devt_period + 12`.

```{r shiny, message=FALSE, warning=FALSE, cache=FALSE}
selectInput(
  "sel_claim",
  "Select Claim number",
  choices = unique(claims$claim_number)[1:50],
  selected = 2008146184
)

plot_data <- reactive({
  indiv <- full_sim[full_sim$claim_number == input$sel_claim, ]
  indiv_act <- claims[claims$claim_number == input$sel_claim, "tot_pd_incr_act"]
  
  list(
    indiv,
    indiv_act
  )
})

renderPlot({
  ggplot(plot_data()[[1]], aes(x = tot_pd_incr_sim)) +
    geom_histogram(fill = "white", colour = "black") +
    ggtitle(paste0("Histogram of Simulated Incremental Payments for claim ", input$sel_claim)) +
    ylab("Number of Observations") +
    xlab("Incremental Payments") +
    geom_vline(xintercept = plot_data()[[2]], size = 1, 
               colour = "blue", linetype = "longdash") +
    scale_x_continuous(labels = dollar)
})

```

```{r table, cache=FALSE}
claim_stats <- reactive({
  out <- claims[claims$claim_number == input$sel_claim, 3:8]
  
  names(out) <- c("Claim Num", "Status", "Case", "Incemental Payment", "Actual Status", "Actual Payment")
  
  out
}) 

renderTable({
  claim_stats()
  },
  include.rownames = FALSE
)
```

# Conclusion

**WIP**

# Appendices

## A. Software

I used `R`, the free and open source statistical programming
environment, for all the data analysis, model fitting, simulations,
graphics, and data output. 

The `caret` package was used extensively for the heavy lifting predictive modeling. 

Detail of the `R` environment at the time this report is available below:

```{r session_code}
sessionInfo()
```

## Closure Model Summary Statistics

```{r}
summary(cm_model)
```

## Zero Payment Model Summary Statistics}

```{r }
summary(zm_model)
```

## Incremental Payment Model Summary Statistics

```{r }
summary(nzm_model)
```
